Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-19 inst/examples/slidetemplates.Rmd
ok

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Default time span
min.year <- 1488
max.year <- 1828

@@

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed and years limited
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

@@

## Automated data clean-up

@@

- Parse, clean up, enrich, summarise, analyze, visualize, report..

>>>>

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
# Default time span
min.year <- 1488
max.year <- 1828

@@

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed and years limited
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

@@

## Automated algorithms for data clean-up

@@

- Open source tools: parse, clean up, interpret, augment, enrich,
  validate, summarise, analyze, visualize, report..
